Integrating Social Visual Analysis and Deployment with RCloud

### 2015-03-28 casestudies.tex
case study update

\section{Case Study\label{sec:casestudy}: topic visualization in RCloud}

@@

This example application is an implementation of LDAVis, a
recently-published method for visualizing large collections of
text. It was specifically designed to enable non-expert users to
explore collections of short text documents using topic modeling and
visualization. Topic modeling~\cite{Blei:2003:LDA} is a standard
technique for text summarization which, although powerful, requires a
certain amount of manual intervention and
interpretation~\cite{Siever:2014:LAM}.

@@

LDAVis itself was developed by two members of the technical staff at
AT\&T Labs, and originally was developed entirely in RStudio's
Shiny~\cite{RStudio:2013:SWA}, a framework for developing R
applications for the web. The main reason for moving the application
to an RCloud development was precisely ease of deployment. Shiny
provides ease of development, but when the application is finished,
one needs to find a publicly available web server that can host the
Shiny application; user management needs to be handled, and so
on. Using RCloud, deployment happens transparently. This is a big win
in terms of efficiency.

Describe the application and the technologies. Runs code from an R
package and custom analysis code; files are uploaded from the web
client, results are provided in JSON format and visualized in the web
client using d3~\cite{Bostock:2011:DDD}.

>>>>

\section{Case Study\label{sec:casestudy}: visual exploration of topic modeling in RCloud}

@@

This example application is an implementation of LDAVis, a
recently-published method for visualizing large collections of
text. It was specifically designed to enable non-expert users to
explore collections of short text documents using topic modeling and
visualization. Topic modeling~\cite{Blei:2003:LDA} is a standard
technique for text summarization which, although powerful, requires a
certain amount of manual intervention and
interpretation~\cite{Sievert:2014:LAM}.

@@

LDAVis itself was developed by two members of the technical staff at
AT\&T Labs, and originally targeted RStudio's
Shiny~\cite{RStudio:2013:SWA}, a framework for developing R
applications for the web.  While Shiny provides unparalleled ease of
development, discoverability and deployment turns out to be equally
important aspects in the lifecycle of an internal application (see
Section~\ref{sec:interviews}).  On these aspects, RCloud provides a
very simple model: \emph{all developed notebooks are automatically
  deployed}.

LDAVis combines textual analysis, dimensionality reduction, and
interactive visualization. The text analysis is performed via a
combination of an existing R library that fits an LDA model using
Gibbs sampling~\cite{} and some R code written specifically by the
developers. The analysis module is, ultimately, a single R function
that is exposed to the web application via the Javascript-R RPC
mechanism described in Section~\ref{sec:system}; this way, the
analysis is executed remotely on the RCloud servers.

Each textual topic is a probability distribution over the all the
words of the document. In order to expose patterns in the
relationships between the topics, LDAVis employs a combination of
interactive visualization and dimensionality reduction (letting users
choose different measures for the topic distances and different
dimensionality reduction techniques). The dimensionality reduction
algorithms and distance measures are again implemented in R, which
means they are executed on the RCloud servers as well.

The result of the dimensionality reduction is a two-dimensional plot
of the topic space, which can be seen in
Figure~\ref{fig:textvis}. Describe d3 view.

This application is simple, but highlights some of the unique features
of RCloud. While RCloud notebooks allow deployment of R analyses over
the web with no additional effor, RCloud \emph{applications} are more
powerful, and are developed in a combination of Javascript and HTML
for the front end. This requires additional knowledge than Shiny, but
we argue that the RCloud model makes the analysis side simpler for the
analysts (since they simply write the R code in the style they are
used to), and the front-end visualization side simpler for the
front-end developers (since they simply write the Javascript code in
the style \emph{they} are used to). In addition, RCloud applications
inherit the automatic deployment and discoverability features of
regular RCloud notebooks.
